---
title: 'Weekly Exercises #6'
author: "Gugo"
output: 
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
    df_print: paged
    code_download: true
---


```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
```

```{r libraries}
library(tidyverse)     # for data cleaning and plotting
library(gardenR)       # for Lisa's garden data
library(lubridate)     # for date manipulation
library(openintro)     # for the abbr2state() function
library(palmerpenguins)# for Palmer penguin data
library(maps)          # for map data
library(ggmap)         # for mapping points on maps
library(gplots)        # for col2hex() function
library(RColorBrewer)  # for color palettes
library(sf)            # for working with spatial data
library(leaflet)       # for highly customizable mapping
library(ggthemes)      # for more themes (including theme_map())
library(plotly)        # for the ggplotly() - basic interactivity
library(gganimate)     # for adding animation layers to ggplots
library(gifski)        # for creating the gif (don't need to load this library every time,but need it installed)
library(transformr)    # for "tweening" (gganimate)
library(shiny)         # for creating interactive apps
library(patchwork)  # for nicely combining ggplot2 graphs 
library(gt)            # for creating nice tables
library(rvest)         # for scraping data
library(robotstxt)     # for checking if you can scrape data
theme_set(theme_minimal())
```

```{r data}
# Lisa's garden data
data("garden_harvest")

#COVID-19 data from the New York Times
covid19 <- read_csv("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv")

```


1. Read in the fake garden harvest data. Find the data [here](https://github.com/llendway/scraping_etc/blob/main/2020_harvest.csv) and click on the `Raw` button to get a direct link to the data. After reading in the data, do one of the quick checks mentioned in the tutorial.

```{r}
garden_harvest %>% 
  mutate(across(where(is.character), as.factor)) %>% 
  summary()
```

  
2. Read in this [data](https://www.kaggle.com/heeraldedhia/groceries-dataset) from the kaggle website. You will need to download the data first. Save it to your project/repo folder. Do some quick checks of the data to assure it has been read in appropriately.

```{r}
groceries_data <- read_csv("Groceries_dataset.csv")
summary(groceries_data)
```

3. Create a table using `gt` with data from your project or from the `garden_harvest` data if your project data aren't ready. Use at least 3 `gt()` functions.

```{r}
 tab<-
  garden_harvest %>% 
  gt()
```

```{r,}
tab2 <- 
  tab %>% 
  fmt_date(columns = c(date),
           date_style = "day_m_year" )
```

```{r}
tab3<-
  tab2 %>% 
  cols_move_to_start(columns = c(date)) 
```

```{r}
tab4<-
  tab3 %>% 
  cols_hide(columns = c(units)) %>% 
  cols_label(weight= "weight in grams")
```



5. Use `patchwork` operators and functions to combine at least two graphs using your project data or `garden_harvest` data if your project data aren't read.
  
```{r,eval=FALSE,fig.width=10, fig.height=6}
g1<-garden_harvest %>% 
  filter(vegetable %in% c("peas")) %>%
  group_by(date, variety) %>%
  summarize(daily_weight=sum(weight)) %>%
  mutate(lbs_daily_weight = daily_weight * 0.00220462, 
         cum_lbs_weight = cumsum(lbs_daily_weight))%>%
  ggplot(aes(x=date, y= lbs_daily_weight,
             color=variety))+
  geom_line()+
  labs(title="The relationship of daily harvest(lbs) between two types of peas", x=element_blank(), y= element_blank())+
  theme_classic()

g2<- garden_harvest %>% 
  filter(vegetable %in% "peas") %>% 
  group_by(variety) %>% 
  summarize(total_harvest_lb = sum(weight)*0.00220462) %>% 
  ggplot(aes(x = total_harvest_lb, 
             y = fct_reorder(variety, total_harvest_lb, .desc = FALSE), 
             fill = variety)) +
  geom_col()+
   labs(x = "Pounds", 
       y = "",
       title = "Total harvest (lb)")

g1+g2+
plot_annotation(title="Perfect Garden Graphs")

```

  
  
  
## Webscraping exercise (also from tutorial)

Use the data from the [Macalester Registrar's Fall 2017 Class Schedule](https://www.macalester.edu/registrar/schedules/2017fall/class-schedule/#crs10008) to complete all these exercises.

6. Find the correct selectors for the following fields. Make sure that each matches 762 results:

  * Course Number
  * Course Name
  * Day
  * Time
  * Room
  * Instructor
  * Avail. / Max
  * General Education Requirements (make sure you only match 762; beware of the Mac copyright banner at the bottom of the page!)
  * Description


Then, put all this information into one dataset (tibble or data.frame) Do not include any extraneous information like "Instructor: ".

```{r}
registrar_data <-read_html("https://www.macalester.edu/registrar/schedules/2017fall/class-schedule/#crs10008")
registrar_data
```

```{r}
course_numbers <- 
  registrar_data %>%
  html_elements(".class-schedule-course-number") %>%
  html_text2()

course_names <- 
  registrar_data %>%
  html_elements(".class-schedule-course-title") %>%
  html_text2()

course_day <- 
  registrar_data %>% 
  html_elements(".class-schedule-course-title+ .class-schedule-label")%>% 
  html_text2()

course_time <- 
  registrar_data %>% 
  html_elements(".class-schedule-label:nth-child(4)") %>% 
  html_text2()

course_room <- 
  registrar_data %>% 
  html_elements(".class-schedule-label:nth-child(5)") %>% 
  html_text2()

course_instructor <- 
  registrar_data %>% 
  html_elements(".class-schedule-label:nth-child(6)") %>% 
  html_text2

course_availability <- 
  registrar_data %>% 
  html_elements(".class-schedule-label:nth-child(7)") %>% 
  html_text2()

course_gen_require <- 
  registrar_data %>% 
  html_elements("#content p:nth-child(2)") %>% 
  html_text2()

course_descripition <- 
  registrar_data %>% 
  html_elements(".collapsed p:nth-child(1)") %>% 
  html_text2()
```


```{r}
courses_registrar <- tibble(number=course_numbers, 
                    name=course_names, 
                    days=course_day, 
                    time=course_time, 
                    room=course_room,
                    availability=course_availability, 
                    gen_requirement=course_gen_require,
                    description=course_descripition)
courses_registrar
```

7. Create a graph that shows the number of sections offered per department. Hint: The department is a substring of the course number - there are `str_XXX()` functions that can help. Yes, COMP and MATH are the same department, but for this exercise you can just show the results by four letter department code, e.g., with COMP and MATH separate.

```{r}
course_departments<-courses_registrar %>% 
  mutate(department = number) %>% 
  mutate(department = str_remove_all(department, " ")) %>% 
  mutate(department = str_remove_all(department, "[1234567890]")) %>% 
  mutate(department = str_remove_all(department, "-")) %>% 
  mutate(department = str_replace_all(department, "RUSSL", "RUSS")) %>%
  mutate(department = str_replace_all(department, "FRENL", "FREN")) %>% 
  mutate(department = str_replace_all(department, "BIOLL", "BIOL")) %>% 
  mutate(department = str_replace_all(department, "CHEML", "CHEM")) %>% 
  mutate(department = str_replace_all(department, "CHINL", "CHIN")) %>% 
  mutate(department = str_replace_all(department, "CLASL", "CLAS")) %>% 
  mutate(department = str_replace_all(department, "MUSIVM", "MUSI")) %>%
  mutate(department = str_replace_all(department, "MUSIMQ", "MUSI")) %>%
  mutate(department = str_replace_all(department, "COMPL", "COMP")) %>% 
  mutate(department = str_replace_all(department, "ECONL", "ECON")) %>%
  mutate(department = str_replace_all(department, "EDUCL", "EDUC")) %>% 
  mutate(department = str_replace_all(department, "ENVIL", "ENVI")) %>% 
  mutate(department = str_replace_all(department, "GEOGL", "GEOG")) %>% 
  mutate(department = str_replace_all(department, "GEOLL", "GEOL")) %>%
  mutate(department = str_replace_all(department, "GERML", "GERM")) %>%
  mutate(department = str_replace_all(department, "HISPL", "HISP")) %>%
  mutate(department = str_replace_all(department, "JAPAL", "JAPA")) %>%
  mutate(department = str_replace_all(department, "MUSIL", "MUSI")) %>%
  mutate(department = str_replace_all(department, "PHYSL", "PHYS")) %>%
  mutate(department = str_replace_all(department, "PSYCL", "PSYC")) %>%
  mutate(department = str_replace_all(department, "THDAL", "THDA"))
```





```{r,fig.height=5, fig.width=10}
  course_departments %>% 
  group_by(department) %>% 
  ggplot(aes(x=department, fill = department)) +
  geom_bar() +
  labs(x ="Department", 
       y = "", 
       title = "The number of sections per deparment in Fall 2017") +
  theme_minimal()+
  guides(fill="none")
```

According to the graph above, Hispanic deparment offered the most sections while Educational Studies offered the least number of sections.

8. Analyze the typical length of course names by department. To do so, create a new data table based on your courses data table, with the following changes:
  
  * New columns for the length of the title of a course and the length of the description of the course. Hint: `str_length`.  
  
    * Remove departments that have fewer than 10 sections of courses. To do so, group by department, then remove observations in groups with fewer than 10 sections (Hint: use filter with n()). Then `ungroup()` the data.  
  
  
```{r}
lengths <- course_departments %>% 
  mutate(title_length = str_length(name)) %>%
  mutate(description_length = str_length(description)) %>% 
  group_by(department) %>%
  filter(n()>10) %>% 
  ungroup()
```
  
 * Create a visualization of the differences across groups in lengths of course names or course descriptions. Think carefully about the visualization you should be using!

```{r,eval=FALSE}
name_departments <- lengths %>%
  group_by(department) %>% 
  summarise(averagetitle = mean(title_length)) %>% 
  ggplot(aes(y = averagetitle, 
             x = reorder(department,-averagetitle), 
             fill = department)) +
    geom_col() + 
    labs(x = "Department", 
       y = "Average Course Name Length", 
       title = "Length of course name by Departments") + 
    guides(fill="none") + 
    theme_minimal()

ggplotly(name_departments)

```
  


  
 *GitHub: 
